### 2022-12-10 ms.rmd
Nothing really

    model3.9_f  <- metafor::rma.mv(effect_size ~ c_accl_time + cv_c, V = V,
                                       random = list(~1 | record_num,
                                            ~1 | species_full,
                                            ~1 | trait,
                                            ~1 | spp,
                                            ~1 | obs),
                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
                              test = "t", data = lnRRQ10_data_wild_acclim_f)
       # Model just quickly tests if we are missing an important interaction. It may not necessarily be just about the variability. We could have variable sites, but a variance site that has some predictability vs a variable site without predictability are two different things. We want predictability AND variance 
     model3.10_f  <- metafor::rma.mv(effect_size ~ c_accl_time + cv_c + acf_all_c + acf_all_c:cv_c, V = V,
                                       random = list(~1 | record_num,
                                            ~1 | species_full,
                                            ~1 | trait,
                                            ~1 | spp,
                                            ~1 | obs),
                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
                              test = "t", data = lnRRQ10_data_wild_acclim_f)

@@

    model3.9_m  <- metafor::rma.mv(effect_size ~ c_accl_time + cv_c, V = V,
                                       random = list(~1 | record_num,
                                            ~1 | species_full,
                                            ~1 | trait,
                                            ~1 | spp,
                                            ~1 | obs),
                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
                              test = "t", data = lnRRQ10_data_wild_acclim_m)
    # Model just quickly tests if we are missing an important interaction. It may not necessarily be just about the variability. We could have variable sites, but a variance site that has some predictability vs a variable site without predictability are two different things. We want predictability AND variance
    model3.10_m  <- metafor::rma.mv(effect_size ~ c_accl_time + cv_c + acf_all_c + acf_all_c:cv_c, V = V,
                                       random = list(~1 | record_num,
                                            ~1 | species_full,
                                            ~1 | trait,
                                            ~1 | spp,
                                            ~1 | obs),
                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
                              test = "t", data = lnRRQ10_data_wild_acclim_m)

>>>>

    model3.9_f  <- metafor::rma.mv(effect_size ~ c_accl_time + cv_c, V = V,
                                       random = list(~1 | record_num,
                                            ~1 | species_full,
                                            ~1 | trait,
                                            ~1 | spp,
                                            ~1 | obs),
                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
                              test = "t", data = lnRRQ10_data_wild_acclim_f)
       # Model just quickly tests if we are missing an important interaction. It may not necessarily be just about the variability. We could have variable sites, but a variance site that has some predictability vs a variable site without predictability are two different things. We want predictability AND variance

     model3.10_f  <- metafor::rma.mv(effect_size ~ c_accl_time + cv_c + acf_all_c + acf_all_c:cv_c, V = V,
                                       random = list(~1 | record_num,
                                            ~1 | species_full,
                                            ~1 | trait,
                                            ~1 | spp,
                                            ~1 | obs),
                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
                              test = "t", data = lnRRQ10_data_wild_acclim_f)

@@

    model3.9_m  <- metafor::rma.mv(effect_size ~ c_accl_time + cv_c, V = V,
                                       random = list(~1 | record_num,
                                            ~1 | species_full,
                                            ~1 | trait,
                                            ~1 | spp,
                                            ~1 | obs),
                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
                              test = "t", data = lnRRQ10_data_wild_acclim_m)
    # Model just quickly tests if we are missing an important interaction. It may not necessarily be just about the variability. We could have variable sites, but a variance site that has some predictability vs a variable site without predictability are two different things. We want predictability AND variance

    model3.10_m  <- metafor::rma.mv(effect_size ~ c_accl_time + cv_c + acf_all_c + acf_all_c:cv_c, V = V,
                                       random = list(~1 | record_num,
                                            ~1 | species_full,
                                            ~1 | trait,
                                            ~1 | spp,
                                            ~1 | obs),
                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
                              test = "t", data = lnRRQ10_data_wild_acclim_m)
